Measurement and Probability in Fuzzy Quantum Theories

### 2017-02-04 prop.tex
prop.tex \appendix Updating...

\section{Increasing the Measurement Resource}

@@

\begin{lemma}An interval-valued frame function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
satisfies the following properties:
\begin{itemize}
\item $\bar{f}\left(\lambda\ket{\psi}\right)=\bar{f}\left(\ket{\psi}\right)$
for any $\ket{\psi}\in\mathbb{C}S^{2}$ and $\lambda\in\mathbb{C}S^{0}$.
\item For any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=0}^{2}$,
we have $1\in\sum_{i=0}^{2}\bar{f}\left(\ket{\psi_{i}}\right)$ and
$\left[1,1\right]-\bar{f}\left(\ket{\psi_{i}}\right)\subseteq\bar{f}\left(\ket{\psi_{j}}\right)+\bar{f}\left(\ket{\psi_{k}}\right)$,
where $i$, $j$, and $k$ are any permutations among $0$, $1$,
and $2$.
\end{itemize}
Conversely, if a function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
satisfies the above properties, $\bar{f}$ must be an interval-valued
frame function.\end{lemma}
\begin{proof}
Given a quantum IVPM~$\bar{\mu}$, it is straightforward to verify
that its interval-valued frame function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
satisfies the above properties.

@@

If $\bar{f}$ has a non-empty core, $\bar{f}$ must be in the above
case 1 - 3 so that $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$ contains
no area in $S^{2}$.\footnote{Notice that we only discuss the part of $\bar{f}^{-1}\left(\imposs\right)$
in $S^{2}$. In general, we could discuss the whole $\bar{f}^{-1}\left(\imposs\right)\subseteq\mathbb{C}S^{2}$.
However, restricting to $S^{2}$ enable us to visualize and imagine
easily. Also, if a interval-valued frame function~$\bar{f}$ has
an empty core when restricting to $S^{2}$, $\bar{f}$ has an empty
core on the original space as well. So restricting to $S^{2}$ still
provides some valid results.} In contrast, if $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$ contains
some area in $S^{2}$, it must be the situation of case 4, and $\bar{f}$
has an empty core. Furthermore, the larger the area, the more state
vectors which are inconsistent with any particular Born rule frame
function. Therefore, the area of $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$
could indicate how much $\bar{f}$ deviate from the Born rule frame
functions. In the following paragraphs, we will establish that if
the area of $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$ is big,
then the interval~$\mathscr{I}$ must be coarse. Therefore, if the
interval~$\mathscr{I}$ is finer, then the area of $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$
would be smaller so that $\bar{f}$ is closer to a Born rule frame
function.

In order to simplify the discussion, consider the center of $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$
as the north pole, and assume $\bar{f}$ maps every state whose latitude
is larger than $\theta_{0}$ to impossible.

\begin{definition}Given a vector~$\ket{\psi}\in S^{2}$ with a specified
north pole~$\ket{0}\in S^{2}$, then $\theta\left(\ket{\psi}\right)=\arccos\ip{0}{\psi}$
denotes the latitude of $\ket{\psi}$. Conversely, $\theta^{-1}\left(I\right)=\set{\ket{\psi}\in S^{2}}{\theta\left(\ket{\psi}\right)\in I}$.
For example, $\theta^{-1}\left(\left[\theta_{0},\frac{\pi}{2}\right]\right)=\set{\ket{\psi}\in S^{2}}{\theta_{0}\le\theta\left(\ket{\psi}\right)\le\frac{\pi}{2}}$
contains all states whose latitude is larger than $\theta_{0}$.\end{definition}

\begin{lemma}Given $\theta_{0}\in\left[0,\frac{\pi}{2}\right]$,
if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\theta^{-1}\left(\left[\theta_{0},\frac{\pi}{2}\right]\right)$,
then for any $\ket{\psi_{0}}$ and $\ket{\psi_{1}}\in\theta^{-1}\left(\left[0,\theta_{0}\right]\right)$,
$\bar{f}\left(\ket{\psi_{0}}\right)=\bar{f}\left(\ket{\psi_{1}}\right)$.\end{lemma}

@@

\section{\label{sec:Real-and-Interval}Quantum Real-valued and Interval-valued
Probability Measures}

>>>>

\section{Interval-valued Frame Functions\label{sec:Interval-valued-Frame-Functions}}

@@

\begin{lemma}\label{lemma:interval-valued-frame-function}An interval-valued
frame function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$ satisfies
the following properties:
\begin{itemize}
\item $\bar{f}\left(\lambda\ket{\psi}\right)=\bar{f}\left(\ket{\psi}\right)$
for any $\ket{\psi}\in\mathbb{C}S^{2}$ and $\lambda\in\mathbb{C}S^{0}$.
\item For any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=0}^{2}$,
we have $1\in\sum_{i=0}^{2}\bar{f}\left(\ket{\psi_{i}}\right)$ and
$\left[1,1\right]-\bar{f}\left(\ket{\psi_{i}}\right)\subseteq\bar{f}\left(\ket{\psi_{j}}\right)+\bar{f}\left(\ket{\psi_{k}}\right)$,
where $i$, $j$, and $k$ are any permutations among $0$, $1$,
and $2$.
\end{itemize}
Conversely, if a function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
satisfies the above properties, $\bar{f}$ must be an interval-valued
frame function.\end{lemma}
\begin{proof}
Given a quantum IVPM~$\bar{\mu}$, it is straightforward to verify
that its interval-valued frame function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
satisfies the above properties.

@@

\section{Real Interval-valued Frame Functions}

In order to simplify the discussion, we call a function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$
satisfying conditions in lemma~\ref{lemma:interval-valued-frame-function}
a real interval-valued frame function. Obviously, any results in section~\ref{sec:Interval-valued-Frame-Functions}
still hold if we replace every ``complex'' by ``real,'' in particular,
replace every $\mathbb{C}S^{2}$ by $S^{2}$. Furthermore, since restricting
the domain of a complex interval-valued frame function to $S^{2}$
gives a real interval-valued frame function, if we prove there is
no real interval-valued frame function satisfying a condition, then
there must be no complex interval-valued frame function satisfying
a corresponding condition. From now on, when we write an interval-valued
frame function~$\bar{f}$, we would always means a real interval-valued
frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$ without other
specification.

If $\bar{f}$ has a non-empty core, $\bar{f}$ must be in the case
1 - 3 in the end of section~\ref{sec:Interval-valued-Frame-Functions}
so that $\bar{f}^{-1}\left(\imposs\right)$ contains no area in $S^{2}$.
In contrast, if $\bar{f}^{-1}\left(\imposs\right)$ contains some
area in $S^{2}$, it must be the situation of case 4, and $\bar{f}$
has an empty core. Furthermore, the larger the area, the more state
vectors which are inconsistent with any particular Born rule frame
function. Therefore, the area of $\bar{f}^{-1}\left(\imposs\right)$
could indicate how much $\bar{f}$ deviate from the Born rule frame
functions. In the following paragraphs, we will establish that if
the area of $\bar{f}^{-1}\left(\imposs\right)$ is big, then the interval~$\mathscr{I}$
must be coarse. Therefore, if the interval~$\mathscr{I}$ is finer,
then the area of $\bar{f}^{-1}\left(\imposs\right)$ would be smaller
so that $\bar{f}$ is closer to a Born rule frame function.

In order to simplify the discussion, consider the center of $\bar{f}^{-1}\left(\imposs\right)$
as the north pole, and assume $\bar{f}$ maps every state whose latitude
is larger than $\theta_{0}$ to impossible.

\begin{definition}Given a vector~$\ket{\psi}\in S^{2}$ with a specified
north pole~$\ket{0}\in S^{2}$, then $\angle\left(\ket{\psi}\right)=\arccos\ip{0}{\psi}$
denotes the latitude of $\ket{\psi}$. Conversely, $\angle^{-1}\left(I\right)=\set{\ket{\psi}\in S^{2}}{\angle\left(\ket{\psi}\right)\in I}$.
For example, $\angle^{-1}\left(\left[\theta_{0},\frac{\pi}{2}\right]\right)=\set{\ket{\psi}\in S^{2}}{\theta_{0}\le\angle\left(\ket{\psi}\right)\le\frac{\pi}{2}}$
contains all states whose latitude is larger than $\theta_{0}$.\end{definition}

\begin{lemma}Given $\theta_{0}\in\left[0,\frac{\pi}{2}\right]$,
if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[\theta_{0},\frac{\pi}{2}\right]\right)$,
then for any $\ket{\psi_{0}}$ and $\ket{\psi_{1}}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
$\bar{f}\left(\ket{\psi_{0}}\right)=\bar{f}\left(\ket{\psi_{1}}\right)$.\end{lemma}

@@

\section{Quantum Real-valued and Interval-valued Probability Measures\label{sec:Real-and-Interval}}
